Meta-analysis

### 2020-05-29 04_MetaAnalysis.Rmd
metafor iterations changed to run as a job script

The first table in this output shows the tau^2 (variance) of each random effects and the number of occurances for each treatment in the analysis. The second table is in two parts(left and right). The left part indicates the level of acceptable rho (variation) when comparing treatments. All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, `0.000` rho. `Early` and `Late_plus` treatments never occured within the same trial which is indicated by the right side of the table.

>>>>

```{r Initiak_ReRunMetafor}
dat1 <- data.frame(
   iteration = 0,
   mods = names(coef(PM_mv_AI)),
   coefs = coef(PM_mv_AI),
   se = PM_mv_AI$se,
   zval = PM_mv_AI$zval,
   pval = PM_mv_AI$pval,
   ci.lb = PM_mv_AI$ci.lb,
   ci.ub = PM_mv_AI$ci.ub,
   row.names = NULL
   )

write.csv(dat1, "./cache/metaIteration.csv", row.names = FALSE)
```

```{r run_iterations_asJobscript}
# WARNING don't run a high number of iterations without increasing sys.sleep
# sys.sleep should not be reduced below 4 for 50 iterations and
# below 0.5 for 10 iterations
for(ITERATE in 1:10){
rstudioapi::jobRunScript(
  "./R/ReRun_metafor-grainyield.R",
  workingDir = here::here(),
  name = "metafor_iteration",
)
   Sys.sleep(1)
}
```

```{r coef_iteration}
dat1 <- read.csv("./cache/metaIteration.csv")
table(dat1$iteration)
dat1 %>%
   ggplot(aes(x = iteration ,y = coefs,))+
   geom_ribbon(aes(ymax = ci.ub, ymin = ci.lb, x = iteration), fill = "grey70")+
   geom_line()+
   facet_grid(cols = vars(mods))

```{r pval_iteration_plot}
dat1 %>%
   ggplot(aes(x = iteration ,y = pval,))+
   geom_line()+
   geom_hline(yintercept = 0.05, colour = "grey50", linetype = 2)+
   facet_grid(cols = vars(mods))

The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis. The second table is in two parts(left and right). The left part indicates the level of acceptable rho (variation) when comparing treatments. All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, `0.000` rho. `Early` and `Late_plus` treatments never occured within the same trial which is indicated by the right side of the table.
